%!TEX root = 0_architecture_rapport.tex

% subsection title
\subsection{Question 1}
\label{subsec:411}

\paragraph{}The database is composed of 7 tables which are given below. Italic attributes are the keys of the table.

\paragraph{Profile table}\textit{playerid} (varchar[12]), name (varchar[56]), position1 (varchar[2]), position2 (varchar[2]), position3 (varchar[2]), shoots (char[1]), height (integer), weight (integer), dob (date), city (varchar[56]), state (varchar[56]), experience (integer) and dod (date).

\paragraph{Totals table}\textit{playerid} (varchar[12]), season (integer), age (integer), team (char[3]), position (varchar[6]), g (integer), gs (integer), mp (integer), fg (integer), fga (integer), fg\_percent (double), three\_point (integer), three\_point\_a (integer), three\_point\_percent (double), two\_point (integer), two\_point\_a (integer), two\_point\_percent (double), efg\_percent (double), ft (integer), fta (integer), ft\_percent (double), orb (integer), drb (integer), trb (integer), ast (integer), stl (integer), blk (integer), tov (integer), pf (integer) and pts (integer).

\paragraph{Per Game table}The schema of this table is the same as Totals table except the \texttt{efg\_percent} attribute which is absent from Per Game table.

\paragraph{Salary table}\textit{playerid} (varchar[12]), season (integer), team (varchar[24]), league (char[3]) and salary (integer).

\paragraph{Team Information table}\textit{franchiseid} (char[3]), city (varchar[24]), state (varchar[24]), season (integer), first\_season (integer), last\_season (integer), wins (integer), losses (integer), winlose\_percent (double), playoff\_app (integer) and championships (integer).

\paragraph{Team Map table}\textit{teamid} (varchar[12]) and team\_name (varchar[128]).

\paragraph{Team Statistics table}\textit{franchiseid} (varchar[12] NOT NULL), \textit{season} (integer), league (char[3]), teamid (char[3] NOT NULL), win (integer), loss (integer), wl_percent (double), finish (integer), srs (double), pace (double), rel_pace (double), ortg (double), rel_ortg (double), drtg (double), rel_drtg (double) and playoffs (varchar[128]).

\paragraph{Team Roster table}\textit{teamid} (char[3] NOT NULL), season (integer), number (varchar[6]), playerid (varchar[12] NOT NULL), position (varchar[6]) and experience (integer).

\paragraph{Active Players table}\textit{playerid} (varchar[12]) and active (varchar[12]).

